Extended Formal Analysis of the EDHOC Protocol in Tamarin

### 2022-07-22 paper.tex
Fixed quote marks in code
[fix] title, authors, affiliations etc

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}

\usepackage{epsfig}
\usepackage{subcaption}
\usepackage{calc}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{multicol}
\usepackage{pslatex}
\usepackage{apalike}

\usepackage[scaled=0.8]{helvet}    % Less huge \textsf{functionName}
\usepackage[misc,geometry]{ifsym} % for letter symbol
\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage{tikz}
\usetikzlibrary{trees,snakes,arrows}
\usetikzlibrary{shapes,chains}
\usetikzlibrary{positioning}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    citecolor=blue,
    urlcolor=blue
}
\usepackage[nospace]{cite}

@@

\title{Formal Analysis of EDHOC Key Establishment for Constrained IoT 
Devices}
\author{
        Karl Norrman and 
        Vaishnavi Sundararajan and
        Alessandro Bruni
}

\begin{document}
\maketitle
%
\begin{abstract}
Given how common IoT devices that use constrained resources are becoming 
today, the need of the hour is communication protocols which can operate 
securely under such limitations.
%
For a few years, the Internet Engineering Task Force (IETF) has been working 
to standardize \mEdhoc{}, an authenticated key establishment protocol for 
such constrained IoT devices.
%
The first version of \mEdhoc{} was proposed in 2016.
%
In 2018, Bruni et al.~\cite{DBLP:conf/secsr/BruniJPS18} used the \mProverif{} 
tool~\cite{DBLP:conf/csfw/Blanchet01} to formally analyze an early version of 
\mEdhoc{}, which had only two key establishment methods.  
%
%By now, the protocol has been fleshed out much more, and has been 
%augmented with multiple new key establishment methods.
By 2021, the protocol had been fleshed out much more, with multiple new key 
establishment methods, and this version was formally analyzed using the 
\mTamarin{} prover~\cite{DBLP:conf/cav/MeierSCB13} in~\cite{Norr21}.
%
Here, we build on this work, by modifying the model, adding new properties 
that we analyze, and discussing some of the aspects of the latest \mEdhoc{} 
specification. In particular, we extend the modelling with trusted execution 
environments (TEEs), modify the way we model \mXor{} encryption, and 
verify weak post-compromise security (PCS) as well as the secrecy and 
integrity of some additional data used as part of the protocol.
\end{abstract}
%
%-------------------------------------------------------------------------- sec
\section{\uppercase{Introduction}}
\label{sec:introduction}
\input{intro}

>>>>

% !TEX TS-program = pdflatexmk

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
\usepackage[T1]{fontenc}

\usepackage{epsfig}
%\usepackage{subcaption}
\usepackage{calc}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{multicol}
\usepackage{pslatex}
\usepackage{apalike}

\usepackage[scaled=0.8]{helvet}    % Less huge \textsf{functionName}
\usepackage[misc,geometry]{ifsym} % for letter symbol
\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage{tikz}
%\usetikzlibrary{trees,snakes,arrows}
\usetikzlibrary{trees,arrows}
\usetikzlibrary{shapes,chains}
\usetikzlibrary{positioning}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    citecolor=blue,
    urlcolor=blue
}
\usepackage[nospace]{cite}

@@

\begin{document}
\title{Extended Formal Analysis of the EDHOC Protocol in Tamarin}
\author{
    Karl Norrman\inst{1,2}\orcidID{0000-0003-0164-1478} \and
    Vaishnavi Sundararajan\inst{3} \and
    Alessandro Bruni\inst{4}
}
\authorrunning{Norrman, Sundararajan and Bruni}
\institute{
    KTH Royal Institute of Technology, Stockholm, Sweden \and
    Ericsson Research, Security, Stockholm, Sweden\\
    \email{karl.norrman@ericsson.com} \and
    University of California Santa Cruz, USA\\
    \email{vasundar@ucsc.edu} \and
    IT University of Copenhagen, Copenhagen, Denmark\\
    \email{brun@itu.dk}
}

\maketitle
%

\begin{abstract}
Given how common IoT devices that use constrained resources are becoming 
today, the need of the hour is communication protocols which can operate 
securely under such limitations.
%
For a few years, the Internet Engineering Task Force (IETF) has been working 
to standardize \mEdhoc{}, an authenticated key establishment protocol for 
such constrained IoT devices.
%
The first version of \mEdhoc{} was proposed in 2016.
%
In 2018, Bruni et al.~\cite{DBLP:conf/secsr/BruniJPS18} used the \mProverif{} 
tool~\cite{DBLP:conf/csfw/Blanchet01} to formally analyze an early version of 
\mEdhoc{}, which had only two key establishment methods.  
%
%By now, the protocol has been fleshed out much more, and has been 
%augmented with multiple new key establishment methods.
By 2021, the protocol had been fleshed out much more, with multiple new key 
establishment methods, and this version was formally analyzed using the 
\mTamarin{} prover~\cite{DBLP:conf/cav/MeierSCB13} in~\cite{Norr21}.
%
Here, we build on this work, by modifying the model, adding new properties 
that we analyze, and discussing some of the aspects of the latest \mEdhoc{} 
specification. In particular, we extend the modelling with trusted execution 
environments (TEEs), modify the way we model \mXor{} encryption, and 
verify weak post-compromise security (PCS) as well as the secrecy and 
integrity of some additional data used as part of the protocol.
\keywords{Formal Verification, Symbolic Dolev-Yao Model,
           Authenticated Key Establishment, Protocols, IoT, Tamarin.}

\end{abstract}
%
%-------------------------------------------------------------------------- sec
\section{\uppercase{Introduction}}
\label{sec:introduction}
\input{intro}
